Reducing Acceptance Marks \\ in Emerson-Lei Automata

### 2021-10-13 paper/main.tex
folding marks added
zacatek intra, opravy v bibu

%{{{ Title and authors

\title{Reducing Acceptance Condition\\ of Emerson-Lei Automata}
\authorrunning{T.~Schwarzová and J. Strej\v{c}ek}
 \author{Tereza Schwarzová \and Jan Strej\v{c}ek}
 \institute{%
   Masaryk University, Brno, Czech Republic\\ \email{\{xschwar3,strejcek\}@mail.muni.cz}
 }

@@

%{{{ Abstract

@@

\section{Introduction}
\begin{itemize}
\item Emerson-Lei automata jsou v principu staré, ale v poslední době
  znovuobjevene~\cite{babiak.15.cav} a je o tom ted spousta
  clanku~\cite{baier.19.atva} a nastroju
\item algoritmy jsou obvykle citlive na akceptacni podminku (citace)
\item cilem prace je zjednodusit akceptacni podminku (zejmnena
  redukovat pocet akceptacnich znacek) bez zmeny struktury automatu
\end{itemize}

@@

@@

\begin{enumerate}
	\item Let $\psi'$ denote the future acceptance condition of $\mathcal{A}'$ and $\psi_{i}$ is the acceptance condition of $S_{i}$ chosen to be merged. Then the algorithm uses \emph{linear sum assignment} to determine which disjunct of $\psi_{i}$ is merged with which disjunct of $\psi'$. The process of using \emph{linear sum assignment} and the pairing procedure is described in detail in work by T. Šťastná \cite{ts_simpl}.
    \item Let $D_{K} \in \overline{\psi_{i}}$ be a disjunct paired with $D_{L} \in \overline{\psi'}$. All conjuncts of $D_{L}$ are initially labeled as unused. Now the algorithm maps every conjunct $C_{k} \in D_{K}$ to a suitable conjunct $C_{l} \in D_{L}$ and labels $C_{l}$ as used. \footnote{The indexes differ to emphasize the fact that they are not equal.} A conjunct $C_{l}$ is suitable for $C_{k}$ is it is on the same type ($\Fin$ or $\Inf$), it is labeled as unused. If no suitable $C_{l}$ is found, the algorithm adds $C_{k}$ to disjunct $D_{L}$ and marks it as used.
\end{enumerate}

@@

@@

@@

>>>>

%{{{ title and authors

\title{Reducing Acceptance Marks \\ in Emerson-Lei Automata}
\authorrunning{T.~Schwarzová and J. Strej\v{c}ek}
 \author{Tereza Schwarzová \and Jan Strej\v{c}ek}
 \institute{%
   Masaryk University, Brno, Czech Republic\\ \email{\{xschwar3,strejcek\}@mail.muni.cz}
 }

@@

%{{{ abstract

@@

%{{{ introduction

\section{Introduction}

Automata over infinite words (also known as $\omega$-automata) are now
used mainly in specification, verification, analysis, monitoring, and
synthesis of various systems with infinite behaviour. The first and
the most common kind of $\omega$-automata is Büchi
automaton~\cite{buchi.60.clmps} introduced in 1960. Other kinds of
$\omega$-automata have been defined \ldots

\todo{Honza je tu!}

Emerson-Lei automata~\cite{emerson.87.scp} were
introduced Automata over infinite words are studied for decades and
used in many areas of computer science including verification,
controller synthesis, m

Emerson-Lei automata~\cite{emerson.87.scp} were introduced in 
\begin{itemize}
\item Emerson-Lei automata jsou v principu staré, ale v poslední době
  znovuobjevene~\cite{babiak.15.cav} a je o tom ted spousta
  clanku~\cite{baier.19.atva} a nastroju
\item algoritmy jsou obvykle citlive na akceptacni podminku (citace)
\item cilem prace je zjednodusit akceptacni podminku (zejmnena
  redukovat pocet akceptacnich znacek) bez zmeny struktury automatu
\end{itemize}

%}}}
%{{{ preliminaries

@@

%}}}
%{{{ standard reductions

@@

\begin{enumerate}
	\item Let $\psi'$ denote the future acceptance condition of $\mathcal{A}'$ and $\psi_{i}$ is the acceptance condition of $S_{i}$ chosen to be merged. Then the algorithm uses \emph{linear sum assignment} to determine which disjunct of $\psi_{i}$ is merged with which disjunct of $\psi'$. The process of using \emph{linear sum assignment} and the pairing procedure is described in detail in work by T. Šťastná \cite{stastna.19.bc}.
    \item Let $D_{K} \in \overline{\psi_{i}}$ be a disjunct paired with $D_{L} \in \overline{\psi'}$. All conjuncts of $D_{L}$ are initially labeled as unused. Now the algorithm maps every conjunct $C_{k} \in D_{K}$ to a suitable conjunct $C_{l} \in D_{L}$ and labels $C_{l}$ as used. \footnote{The indexes differ to emphasize the fact that they are not equal.} A conjunct $C_{l}$ is suitable for $C_{k}$ is it is on the same type ($\Fin$ or $\Inf$), it is labeled as unused. If no suitable $C_{l}$ is found, the algorithm adds $C_{k}$ to disjunct $D_{L}$ and marks it as used.
\end{enumerate}

@@

%}}}
%{{{ QBF-based reduction

@@

%}}}
%{{{ implementation and experimental evaluation

@@

%}}}
%{{{ conclusion
